---
output:
  html_document: default
  pdf_document: default
---


# Input

```{r}
library(rdhs)
library(dplyr)
library(labelled)
library(tidyr)


load("df_2019.Rda")
df_2019$country <- "RW"
df_2019 <- df_2019 <- df_2019 %>% drop_na(c("hv105", "hv111", "hv113",
                                            "hv104", "country"))
df_2019 <- df_2019 %>% rename(
  "Age" = "hv105",
  "Mother_alive" = "hv111",
  "Father_alive" = "hv113",
  "Sex" = "hv104",
)
df_2019 <- unlabelled(df_2019)
head(df_2019)
```


# Health

## Anemia level
In this variable, 1 means positive, 0 means negative. It only contains teenage female data.

```{r}
df <- df_2019 %>% drop_na(c("ha57"))
table(df$ha57)
glm_anemia <- glm(ha57 ~ Mother_alive + Father_alive + Age,
                  family="binomial", data=df)
summary(glm_anemia)
```


## Malaria

```{r}
df <- df_2019 %>% drop_na(c("hml32"))
table(df$hml32)
glm_malaria <- glm(hml32 ~ Mother_alive + Father_alive + Sex + Age,
                  family="binomial", data=df)
summary(glm_malaria)
```


## Hemoglobin level
This variable is continuous with unit g/dl. It only contains teenage female data.

```{r}
df <- df_2019 %>% drop_na(c("ha56"))
lm_hemoglobin <- lm(ha56 ~ Mother_alive + Father_alive + Age, data=df)
summary(lm_hemoglobin)
```


## Body fit
Consider BMI for individuals with height and weight information. (teenage female)
Q: definition of overweight / underweight also depends on age, sex, ethnic background.

```{r}
df <- df_2019 %>% drop_na(c("ha2", "ha3"))
df$ha3 <- df$ha3 / 1000 # height in m
df$ha2 <- df$ha2 / 10 # weight in kg
df$BMI <- df$ha2 / df$ha3 ^ 2
df$obese <- df$BMI > 30
df$underweight <- df$BMI < 16
table(df$obese)
lm_obese <- lm(obese ~ Mother_alive + Father_alive + Age, data=df)
summary(lm_obese)
table(df$underweight)
lm_underweight <- lm(underweight ~ Mother_alive + Father_alive + Age, data=df)
summary(lm_underweight)
```


# Education

## School attendance
Only consider the status of school attendance. 0 is no, 1 is attending.

```{r}
df <- df_2019 %>% drop_na(c("hv121"))
table(df$hv121)
glm_attainment <- glm(hv121 ~ Mother_alive + Father_alive + Sex + Age,
                      family="binomial", data=df)
summary(glm_attainment)
```


## Highest level of education attended
Only consider the status of school attendance. 0 is no, 1 is attending.

```{r}
df <- df_2019 %>% drop_na(c("hv106"))
table(df$hv106)
glm_edu_level <- glm(hv121 ~ Mother_alive + Father_alive + Sex + Age,
                      family="binomial", data=df)
summary(glm_edu_level)
```


# Sexuality, marriage, and birth history

## Teenage marriage

```{r}
df <- df_2019 %>% drop_na(c("hv115"))
table(df$hv115)
glm_marriage <- glm(hv115 ~ Mother_alive + Father_alive + Sex + Age,
                      family="binomial", data=df)
summary(glm_marriage)
```


## Teenage pregnancy

```{r}
df <- df_2019 %>% drop_na(c("hml18"))
table(df$hml18)
glm_pregnancy <- glm(hml18 ~ Mother_alive + Father_alive + Age,
                     family="binomial", data=df)
summary(glm_pregnancy)
```


Questions:

* Mother alive and father alive are separated explanatory variables?
* problems: interactions, significance
* Colombia data set does not have health data


To do:

* Interpret confidence interval
* Other explanatory variables or interactions




